Constraint Programming Algorithms used in Gecode

### 2014-05-19 paper.tex
corrections Michael

	\subsubsection{Restart Strategies}
	Branching always means to apply certain heuristics and these heuristics may fail or produce bad results for the first execution of the search algorithm. If it turns out that the search tree is build in a disadvantageous way a restart strategy may be appropriate to improve the search. For such a restart the heuristic is improved, based on the things the search has learned to be a not so good solution during the first or first few attempts to build a search tree.
	For practical application several variants of restart strategies were proposed \cite[p.~113]{handbookCP}.

>>>>

	\subsubsection{Restart Strategies}
	Branching always means to apply certain heuristics and these heuristics may fail or produce bad results for the first execution of the search algorithm. If it turns out that the search tree is build in a disadvantageous way a restart strategy may be appropriate to improve the search. For such a restart the heuristic is improved, based on the things the search has learned to be a not so good solution during the first few attempts to build a search tree.
	For practical application several variants of restart strategies were proposed \cite[p.~113]{handbookCP}.
